Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps

### 2014-07-08 ms.tex
comment
starting discussion of EBV residuals, added four-panel figure showing residuals

% do I need to cite a reference the first time that i mention SDSS ?

@@

@@

% cite Green appendix for details of deriving EBV_SSPP from Schlafly 11 data ?

The result of this regression is shown in Figure \ref{fig:calib}. Indeed there 
appears to be a strong linear correlation between $E(B-V)_{SSPP}$ 
and $\tau_{545}$. The conversion factor from $\tau_{545}$ to $E(B-V)$ is 
2.46$\times$10$^{3}$. Reassuringly, the best-fit offset is quite close to 
zero, $\sim$0.6 mmag.

Figure \ref{fig:resid} shows a two-dimensional histogram of the residuals of
the $\tau_{545}$-based $E(B-V)$ predictions relative to the corresponding
spectrum-based $E(B-V)$ predictions, as a function of SFD $E(B-V)$. Clearly 
there are some systematic trends in the residuals. Still, for 
$E(B-V)_{SFD}$$<$0.28 ($\sim$80\% of the sky), the residual median is always 
within 10 mmag of zero. Over the entire range $E(B-V)_{SFD}$$<$0.7, the 
residual median is always within 30 mmag of zero.

\begin{figure}
\begin{center}
\epsfig{file=ebv_resid.eps, width=3.3in}
\caption{\label{fig:resid} $E(B-V)_{2comp}$ residuals as a function of
SFD $E(B-V)$. The grayscale represents the conditional probability within each
bin in SFD $E(B-V)$. The central black line shows the moving median. The upper
and lower black lines represent the moving 75th and 25th percentiles 
respectively.}
\end{center}
\end{figure}

@@

>>>>

@@

\begin{figure*}
\begin{center}
\epsfig{file=ebv_resid.eps, width=6.6in}
\caption{\label{fig:resid} $E(B-V)_{2comp}$ residuals as a function of
SFD $E(B-V)$. The grayscale represents the conditional probability within each
bin in SFD $E(B-V)$. The central black line shows the moving median. The upper
and lower black lines represent the moving 75th and 25th percentiles 
respectively.}
\end{center}
\end{figure*}

@@

% need to explain SSPP acronym somewhere ?
% cite Green appendix for details of deriving EBV_SSPP from Schlafly 11 data ?

This regression is illustrated in Figure \ref{fig:calib}. As expected, there 
appears to be a strong linear correlation between $E(B-V)_{SSPP}$ and 
$\tau_{545}$. The conversion factor from $\tau_{545}$ to $E(B-V)$ is 
2.46$\times$10$^{3}$. Reassuringly, the best-fit offset is quite close to zero,
$\sim$0.6 mmag.

Figure \ref{fig:resid} shows the residuals of our $\tau_{545}$-based reddening 
predictions, $E(B-V)_{2comp}$, relative to the corresponding SF11 reddening 
measurements, $E(B-V)_{SSPP}$, as a function of SFD reddening, $E(B-V)_{SFD}$, 
(top left panel) and as a function of hot dust temperature (bottom left panel).
For comparison, the right panels show analogous residual plots, but with 
respect to reddening predictions based on our calibration of the 
\cite{planckdust} 353 GHz optical depth to $E(B-V)_{SSPP}$ , using the same 
regression procedure employed to calibrate $E(B-V)_{2comp}$. We refer to these 
reddening predictions based on the \cite{planckdust} single-MBB model and 
calibrated to the SF11 measurements as $E(B-V)_{mbb}$.

All four residual plots in Figure 12 show systematic problems at some level. 
The most striking systematic trend is the `bending' behavior of the reddening
residuals versus $E(B-V)_{SFD}$ (top panels), with the median residual 
bottoming out near $-10$ mmag around $E(B-V)_{SFD}$=0.15 mag. This behavior is 
common to both $E(B-V)_{2comp}$ and $E(B-V)_{mbb}$, and in fact was first noted
in the residuals of $E(B-V)_{SFD}$ itself relative to $E(B-V)_{SSPP}$ by SF11 
(see their Figure 6). Such a bending behavior is troubling because it could 
indicate a nonlinearity common to many FIR reddening predictions based on
column densities inferred from dust emission. Alternatively, because the SF11 
stars are distributed over the sky in a highly non-uniform manner, the bend 
could arise from aliasing of discrepancies particular to certain sky regions 
(e.g. inner vs. outer Galaxy) on to the $E(B-V)_{SFD}$ axis.

The obvious culprit for any potential nonlinearity in FIR-based reddening
estimates is a faulty temperature correction. For this reason, we have included
the bottom panels of Figure \ref{fig:resid}, to check for the presence of
a dependence of the reddening residuals on dust temperature.

%Clearly there are some systematic trends in the residuals.
%Still, for $E(B-V)_{SFD}$$<$0.28 ($\sim$80\% of the sky), the residual median 
%is always within 10 mmag of zero. Over the entire range $E(B-V)_{SFD}$$<$0.7, 
%the residual median is always within 30 mmag of zero.

@@

% if we're not going to be claiming to be superseding SFD in terms of 
% reddening, then do we even want to include anything extinction-related
% (data files and/or code) in this data release ?
